Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-12 analysis/paper/Rmd/hotspot-one-chromosome.Rmd
fixed conditional statement for downloading from datadryad

```{r iheatmapr-{{hot_chr}}, out.width="20in"}
ann3 <- annots_ord[[3]] %>%
  ungroup() %>%
  select(- symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[3]]$symbol; return(x)})
colnames(ann3) <- LETTERS[1:8]
ann2 <- annots_ord[[2]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[2]]$symbol; return(x)})
ann1 <- annots_ord[[1]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[1]]$symbol; return(x)})
ann5 <- annots_ord[[5]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[5]]$symbol; return(x)})
ann6 <- annots_ord[[6]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[6]]$symbol; return(x)})
ann4 <- annots_ord[[4]] %>%
  ungroup() %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[4]]$symbol; return(x)})
mymat <- pm[ord, ord] %>% # order both cols and rows by 'ord'
  apply(FUN = trunc2, MARGIN = 2, threshold = 5)
iheatmapr::main_heatmap(mymat, show_colorbar = FALSE, layout = list(font = list(size = 2))) %>%
  iheatmapr::add_col_labels() %>%
  iheatmapr::add_col_annotation(ann5) %>%
  iheatmapr::add_main_heatmap(ann3, name = "signal3", size = 0.2, show_colorbar = FALSE) %>%
    iheatmapr::add_col_labels() %>%

>>>>

```{r iheatmapr-{{hot_chr}}, out.width="25in", out.height = "10in"}
ann3 <- annots_ord[[3]] %>%
  ungroup() %>%
  select(- symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[3]]$symbol; return(x)})
colnames(ann3) <- LETTERS[1:8]
ann2 <- annots_ord[[2]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[2]]$symbol; return(x)})
ann1 <- annots_ord[[1]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[1]]$symbol; return(x)})
ann5 <- annots_ord[[5]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[5]]$symbol; return(x)})
ann6 <- annots_ord[[6]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[6]]$symbol; return(x)})
ann4 <- annots_ord[[4]] %>%
  ungroup() %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[4]]$symbol; return(x)})
mymat <- pm[ord, ord] %>% # order both cols and rows by 'ord'
  apply(FUN = trunc2, MARGIN = 2, threshold = 5)
iheatmapr::main_heatmap(mymat, show_colorbar = FALSE, layout = list(font = list(size = 2))) %>%
  iheatmapr::add_col_labels() %>%
  iheatmapr::add_col_annotation(ann5) %>%
  iheatmapr::add_main_heatmap(ann3, name = "signal3", size = 0.2, show_colorbar = FALSE) %>%
    iheatmapr::add_col_labels() %>%

### 2019-08-12 analysis/paper/Rmd/hotspots-paper.Rmd
added iheatmapr heatmaps to hotspots-paper.Rmd
fixed conditional statement for downloading from datadryad

```{r load_heatmaply}
library(heatmaply)
```

```{r saveRDS}
if (!file.exists(here("analysis", "data", "derived_data", "expr.rds"))){
  download.file("https://datadryad.org/bitstream/handle/10255/dryad.166774/Attie_DO378_eQTL_viewer_v1.Rdata?sequence=2",
              destfile = here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata")
              )
  load(here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata"))
  saveRDS(dataset.islet.rnaseq$lod.peaks, here("analysis", "data", "derived_data", "lod_peaks.rds"))
  saveRDS(dataset.islet.rnaseq$annots, here("analysis", "data", "derived_data", "annots.rds"))
  saveRDS(dataset.islet.rnaseq$expr, here("analysis", "data", "derived_data", "expr.rds"))
  saveRDS(K, here("analysis", "data", "derived_data", "kinship.rds"))
  saveRDS(map, here("analysis", "data", "derived_data", "map.rds"))
  saveRDS(genoprobs, here("analysis", "data", "derived_data", "genoprobs.rds"))
  saveRDS(dataset.islet.rnaseq$covar, here("analysis", "data", "derived_data", "covar.rds"))
}
```

>>>>

```{r saveRDS}
if (!file.exists(here("analysis", "data", "derived_data", "genoprobs.rds"))){
  download.file("https://datadryad.org/bitstream/handle/10255/dryad.166774/Attie_DO378_eQTL_viewer_v1.Rdata?sequence=2",
              destfile = here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata")
              )
  load(here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata"))
  saveRDS(dataset.islet.rnaseq$lod.peaks, here("analysis", "data", "derived_data", "lod_peaks.rds"))
  saveRDS(dataset.islet.rnaseq$annots, here("analysis", "data", "derived_data", "annots.rds"))
  saveRDS(dataset.islet.rnaseq$expr, here("analysis", "data", "derived_data", "expr.rds"))
  saveRDS(K, here("analysis", "data", "derived_data", "kinship.rds"))
  saveRDS(map, here("analysis", "data", "derived_data", "map.rds"))
  saveRDS(genoprobs, here("analysis", "data", "derived_data", "genoprobs.rds"))
  saveRDS(dataset.islet.rnaseq$covar, here("analysis", "data", "derived_data", "covar.rds"))
}
```
